\documentclass[10pt,letterpaper]{article}

% ATS-safe, single-column resume
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[left=0.6in,right=0.6in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{colorlinks=true,urlcolor=black,linkcolor=black}
\pagestyle{empty}
\setlength{\parindent}{0pt}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\vspace{1pt}\hrule\vspace{3pt}]
\titlespacing{\section}{0pt}{3pt}{1pt}

% List formatting
\setlist[itemize]{leftmargin=1.3em,topsep=1pt,itemsep=0pt,parsep=0pt,label=\textbullet}

% Entry header helper: \entry{Title}{Location}{Subtitle}{Dates}
\newcommand{\entry}[4]{%
  \textbf{#1}\hfill #2\\[1pt]
  \textit{#3}\hfill \textit{#4}\\[2pt]
}

\begin{document}

% ===== HEADER =====
\begin{center}
  {\LARGE \textbf{Veer Sanyal}}\\[3pt]
  Sammamish, WA $\cdot$ 360-643-9424 $\cdot$ vsanyal@purdue.edu $\cdot$ linkedin.com/in/veersanyal
\end{center}

\vspace{2pt}
Multidisciplinary visual designer with 4+ years across raster editing, vector illustration, brand identity, and layout (Adobe Creative Suite and open-source equivalents), plus hands-on experience integrating and evaluating generative-AI output. Self-directed, detail-oriented, and comfortable working independently on remote contract work.

% ===== DESIGN EXPERIENCE =====
\section*{Design Experience}
\entry{Etsy Digital Products Shop}{Remote}{Independent Designer \& Shop Owner}{2023 -- Present}
\begin{itemize}
  \item Designed and sold 50+ original digital products (printable and editable planners, habit and fitness trackers, travel checklists, intake and invoice forms) end-to-end as sole designer and operator.
  \item Built a cohesive visual system per product line --- custom layouts, color palettes, and typography across raster and vector workflows --- holding brand consistency across an entire product family.
  \item Produced full marketing media per listing (device mockups, thumbnails, multi-image galleries, a product demo video) and delivered both fillable-PDF and print-ready versions, balancing original design with usability and exacting print specifications.
\end{itemize}

% ===== DESIGN PROJECTS =====
\section*{Design Projects}
\textbf{Graphic Design Portfolio (raster + vector)}\hfill \textit{2021 -- Present}\\[1pt]
\textit{Photoshop, Illustrator, Lightroom --- workflows transfer directly to GIMP, Inkscape, and Krita}
\begin{itemize}
  \item Designed branding and full report layouts for two 10-page DECA business-plan competition papers --- MYCOFIX (custom wordmark and molecular icon mark) and Green Torch Solutions (complete brand identity) --- producing polished, competition-ready documents.
  \item Created original logos and brand-identity explorations for self-initiated concept ventures (BAGBABY, PAPER ELEPHANT) and built vector illustrations and sports graphics (Purdue Pete vs. Oregon Duck mascot vector); retouched professional headshots at 300 PPI using layer masking and background compositing.
\end{itemize}

\textbf{StudyFlowForge --- Independent Product Build}\hfill \textit{Feb. 2026 -- Present}\\[1pt]
\textit{React, TypeScript, Gemini API}
\begin{itemize}
  \item Integrated and evaluated AI-generated content (Gemini API), reviewing model outputs for accuracy, relevance, and quality against written criteria before surfacing them to users --- directly analogous to creating and rating data used to train AI.
  \item Designed and shipped 18 user-facing screens end-to-end --- UX flows, a reusable component library, and visual and information architecture.
\end{itemize}

% ===== ADDITIONAL EXPERIENCE =====
\section*{Additional Experience}
\textbf{Firmly} --- \textit{Product \& Engineering Intern} \hfill \textit{Jun. 2025 -- Aug. 2025}
\begin{itemize}
  \item Reviewed and validated product output against written guidelines across \textasciitilde15 edge cases with close attention to detail; worked independently and asynchronously across time zones.
\end{itemize}

% ===== EDUCATION =====
\section*{Education}
\textbf{Purdue University --- Mitch Daniels School of Business}\hfill West Lafayette, IN\\[1pt]
\textit{B.S. Integrated Business and Engineering (IBE), Expected May 2028}\hfill \textit{Aug. 2024 -- Present}

% ===== LEADERSHIP =====
\section*{Leadership \& Activities}
\textbf{Engineering Projects in Community Service (EPICS)} --- \textit{Communications Officer \& Build Lead} \hfill \textit{Aug. 2025 -- Dec. 2025}
\begin{itemize}
  \item Led a 7-person team and presented design tradeoffs and visual updates to faculty, sponsors, and stakeholders across two formal design reviews.
\end{itemize}

% ===== SKILLS =====
\section*{Skills}
\textbf{Creative Tools:} GIMP, Inkscape, Krita (transferred from 4+ years in Adobe Photoshop, Illustrator, Lightroom); raster editing, vector illustration, pixel and layout design\\[2pt]
\textbf{Design Craft:} Brand identity, logo design, typography, print \& layout design, photo retouching, mockup production, UI/UX design, original visual concepting\\[2pt]
\textbf{AI \& Workflow:} AI-output evaluation \& QA against written guidelines, generative-content workflows, LLM/Gemini API integration; independent async remote work, Excel, PowerPoint, Git/GitHub

\end{document}
