\documentclass[10pt,letterpaper]{article}

% ATS-safe, single-column resume
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[left=0.6in,right=0.6in,top=0.55in,bottom=0.55in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{colorlinks=true,urlcolor=black,linkcolor=black}
\pagestyle{empty}
\setlength{\parindent}{0pt}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\vspace{1pt}\hrule\vspace{3pt}]
\titlespacing{\section}{0pt}{6pt}{2pt}

% List formatting
\setlist[itemize]{leftmargin=1.3em,topsep=1pt,itemsep=1pt,parsep=0pt,label=\textbullet}

% Entry header helper: \entry{Title}{Location}{Subtitle}{Dates}
\newcommand{\entry}[4]{%
  \textbf{#1}\hfill #2\\[1pt]
  \textit{#3}\hfill \textit{#4}\\[2pt]
}

\begin{document}

% ===== HEADER =====
\begin{center}
  {\LARGE \textbf{Veer Sanyal}}\\[3pt]
  Sammamish, WA $\cdot$ 360-643-9424 $\cdot$ vsanyal@purdue.edu $\cdot$ linkedin.com/in/veersanyal
\end{center}

% ===== EDUCATION =====
\section*{Education}
\textbf{Purdue University --- Mitch Daniels School of Business}\hfill West Lafayette, IN\\[1pt]
\textit{B.S. Integrated Business and Engineering (IBE), Expected May 2028}\hfill \textit{Aug. 2024 -- Present}
\begin{itemize}
  \item Relevant Coursework: Financial Accounting, Managerial Accounting, Microeconomics, Statistics, Engineering Design \& Project Execution
\end{itemize}

% ===== EXPERIENCE =====
\section*{Experience}
\entry{Student Managed Investment Fund (SMIF)}{West Lafayette, IN}{Equity Research Analyst}{Jan. 2025 -- Present}
\begin{itemize}
  \item Conducted financial analysis on a public company (U.S. Bancorp) within a \textasciitilde\$400K AUM real-money portfolio; interpreted financial statements to identify revenue drivers, competitive dynamics, and key risks.
  \item Built a 3-statement financial model in Excel (DCF, comps, sensitivity analysis) to quantify profitability across upside and downside scenarios; defended assumptions with analytical rigor under committee questioning.
  \item Co-authored a 20-page client-style equity report recommending Buy at a \$57.35 target (\textasciitilde11.5\% implied upside); led the competitive analysis and risk-assessment sections with close attention to detail.
  \item Distilled segment-level analysis into a 10-slide pitch for a 30+ member investment committee, communicating quantitative reasoning and financial terminology clearly to a mixed-experience audience.
\end{itemize}

\entry{Firmly (Fintech / E-Commerce Platform)}{Remote}{Product and Engineering Intern}{Jun. 2025 -- Aug. 2025}
\begin{itemize}
  \item Reviewed and validated software output against written requirements across \textasciitilde15 high-risk edge cases, applying structured judgment to flag inaccuracies before release.
  \item Built a repeatable QA workflow (20+ test cases plus a release checklist) adopted as the team standard for evaluating output accuracy and consistency across releases.
  \item Worked independently and asynchronously across time zones, following written guidelines and authoring handoff documentation that reduced ambiguity and back-and-forth.
\end{itemize}

% ===== PROJECTS =====
\section*{Projects}
\textbf{StudyFlowForge --- Independent Product Build}\hfill \textit{Feb. 2026 -- Present}\\[1pt]
\textit{React, TypeScript, Supabase (PostgreSQL), Gemini API}
\begin{itemize}
  \item Integrated and evaluated AI-generated content (Gemini API), reviewing model outputs for accuracy and relevance before surfacing them to users --- directly analogous to AI-response evaluation work.
  \item Engineered a multi-factor scoring model (weighted, parameterized inputs with scenario analysis) in TypeScript, mirroring factor-weighting logic used in financial models.
\end{itemize}

% ===== LEADERSHIP =====
\section*{Leadership \& Activities}
\textbf{Engineering Projects in Community Service (EPICS)}\hfill West Lafayette, IN\\[1pt]
\textit{Communications Officer \& Build Lead}\hfill \textit{Aug. 2025 -- Dec. 2025}
\begin{itemize}
  \item Led a 7-person cross-functional team and presented structured tradeoff analyses with supporting data to faculty, sponsors, and stakeholders across two formal design reviews.
\end{itemize}

% ===== SKILLS =====
\section*{Skills}
\textbf{Financial Analysis \& Modeling:} 3-statement modeling, DCF, comps, sensitivity \& scenario analysis, financial statement interpretation, valuation, Excel (pivot tables)\\[2pt]
\textbf{Research \& Communication:} Equity research, client-style written reports, investment pitches, competitive analysis, quantitative reasoning, attention to detail\\[2pt]
\textbf{AI \& Quantitative:} AI-output evaluation \& QA, LLM/Gemini API integration, multi-factor scoring models, SQL, Python\\[2pt]
\textbf{Tools \& Workflow:} PowerPoint, Word, Git/GitHub, independent async remote work, structured handoff documentation

\end{document}
