% Salesforce Summer 2027 Intern - Associate Product Manager (APM), JR348039
% Tailored for AI/agentic PM role: LLMs, autonomous agents, data architecture,
% market/competitor analysis, cross-functional eng+design, stakeholder presentation.
% Compile: pdflatex VeerSanyal_Salesforce_Resume.tex
\documentclass[10pt,letterpaper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[left=0.6in,right=0.6in,top=0.55in,bottom=0.55in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{colorlinks=true,urlcolor=black,linkcolor=black}
\pagestyle{empty}
\setlength{\parindent}{0pt}

\titleformat{\section}{\large\bfseries}{}{0pt}{}[\vspace{1pt}\hrule\vspace{3pt}]
\titlespacing{\section}{0pt}{6pt}{2pt}

\setlist[itemize]{leftmargin=1.3em,topsep=1pt,itemsep=1pt,parsep=0pt,label=\textbullet}

\newcommand{\entry}[4]{%
  \textbf{#1}\hfill #2\\[1pt]
  \textit{#3}\hfill \textit{#4}\\[2pt]
}

\begin{document}

% ===== HEADER =====
\begin{center}
  {\LARGE \textbf{Veer Sanyal}}\\[3pt]
  Sammamish, WA $\cdot$ 360-643-9424 $\cdot$ vsanyal@purdue.edu $\cdot$ linkedin.com/in/veersanyal
\end{center}

% ===== EDUCATION =====
\section*{Education}
\textbf{Purdue University --- Mitch Daniels School of Business}\hfill West Lafayette, IN\\[1pt]
\textit{B.S. Integrated Business and Engineering (IBE), Expected May 2028}\hfill \textit{Aug. 2024 -- Present}
\begin{itemize}
  \item Integrated Business and Engineering: a selective business + engineering hybrid degree. Relevant coursework: Statistics, Engineering Design \& Project Execution, Managerial Accounting, Microeconomics.
\end{itemize}

% ===== EXPERIENCE =====
\section*{Experience}
\entry{Firmly}{Remote}{Product and Engineering Intern}{Jun. 2025 -- Aug. 2025}
\begin{itemize}
  \item Shipped a PayPal checkout failure-recovery flow end-to-end: analyzed user needs, defined requirements, and partnered with senior engineers and UX to launch a guided recovery experience replacing a generic error page.
  \item Validated fixes across \textasciitilde15 high-risk payment edge cases (missing billing/shipping data); built and tracked product metrics (error rate, recovery rate) via server-side logging to drive data-driven decisions.
  \item Built a repeatable QA workflow (edge-case matrix + release checklist, 20+ test cases) adopted as the team standard; authored structured handoff docs that reduced cross-functional back-and-forth.
\end{itemize}

\entry{Student Managed Investment Fund}{West Lafayette, IN}{Equity Research Analyst}{Jan. 2025 -- Present}
\begin{itemize}
  \item Analyzed market trends, competitive dynamics, and revenue drivers for U.S. Bancorp in a \textasciitilde\$400K AUM real-money fund; synthesized research into a 20-page report recommending Buy at a \$57.35 target (\textasciitilde11.5\% implied upside).
  \item Presented the thesis in a 10-slide deck to a 30+ member investment committee and defended assumptions under live questioning; refined revenue and risk framing from stakeholder feedback.
\end{itemize}

% ===== PROJECTS =====
\section*{Projects}
\entry{StudyFlowForge --- AI-Powered Study Planner}{}{Independent product build (React, TypeScript, Supabase, Gemini API)}{Feb. 2026 -- Present}
\begin{itemize}
  \item Defined product strategy and roadmap for an AI planner using LLM-based prioritization (Gemini API) to surface personalized, context-aware study plans from course-calendar data.
  \item Integrated generative AI (Gemini API) into the data pipeline and designed the SQL / PostgreSQL data architecture (Supabase) powering real-time, drillable dashboards on mastery, retention, and at-risk metrics.
  \item Shipped 18 user-facing screens end-to-end as sole developer; ran user research and translated pain points into an exam-aware prioritization engine and exception-handling views.
\end{itemize}

% ===== LEADERSHIP =====
\section*{Leadership \& Activities}
\entry{Engineering Projects in Community Service (EPICS)}{West Lafayette, IN}{Communications Officer \& Build Lead}{Aug. 2025 -- Dec. 2025}
\begin{itemize}
  \item Led a 7-person cross-functional team building a rotating museum billboard prototype; coordinated weekly tasks, translated requirements into build specs, and presented design tradeoffs in two formal reviews to faculty, sponsors, and museum stakeholders.
\end{itemize}

% ===== SKILLS =====
\section*{Skills}
\textbf{Product \& Strategy:} product strategy \& roadmaps, PRDs / specs, market \& competitive analysis, user research, success metrics, cross-functional (eng / UX)\\[2pt]
\textbf{AI \& Data:} LLM / Gemini API integration, generative-AI product integration, Claude Code (AI-assisted development), SQL schema \& data architecture, KPI dashboarding, A/B testing fundamentals\\[2pt]
\textbf{Engineering \& Tools:} Python, HTML/CSS, Git/GitHub; React / TypeScript, Node.js / Express (built with); Excel, PowerPoint

\end{document}
